\textbf{Transparency to hybrid open access through publisher-provided metadata: An article-level study of Elsevier}

### 2021-05-03 analysis/manuscript.Rmd
kableExtra error

```{r subject_profile}
sponsor_country %>%
  ungroup() %>%
  pivot_wider(id_cols = c("country_factor"), names_from = `Primary research focus`, values_from = prop) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  janitor::adorn_totals(c("col", "row")) %>%
  mutate_if(is.numeric, ~paste0(., "%")) %>%
  rename(`Country/Subject area` = country_factor) %>%
  kableExtra::kbl(booktabs = TRUE,
                  caption = " Relative subject profile of centrally invoiced OA funding bodies.", align = c("l|rrrrr|r")) %>%
    row_spec(6:7, hline_after = TRUE) %>%
   kable_styling(latex_options = c("scale_down"))
```

>>>>

```{r subject_profile}
sponsor_country %>%
  ungroup() %>%
  pivot_wider(id_cols = c("country_factor"), names_from = `Primary research focus`, values_from = prop) %>%
  mutate_all(~replace(., is.na(.), 0)) %>%
  janitor::adorn_totals(c("col", "row")) %>%
  mutate_if(is.numeric, ~paste0(., "%")) %>%
  rename(`Country/Subject area` = country_factor) %>%
  kableExtra::kbl(booktabs = TRUE,
                  caption = " Relative subject profile of centrally invoiced OA funding bodies.", align = c("lrrrrrr")) %>%
    row_spec(6:7, hline_after = TRUE) %>%
   kable_styling(latex_options = c("scale_down"))
```
